Reference Tracking Strategies of Native and Late Signers in Turkish Sign Language

### 2022-08-06 revised_manuscript.tex
updated files

We collected 4142 data points as a result of the experiment. Each data
point is a referent tracked by the participant. Each of the REs is
classified in terms of its Discourse Status (Introduction, Maintenance,
Re-introduction), its Type (Nominal, Pronominal, Classifer,
Null)\footnote{In our statistical analyses, we will not consider the subtypes of REs but rather group them by the four proposed main types (Nominal, Pronominal, Classifer, and Null). However, we allude to the numerical distribution of the subtypes in this and following sections},
and Participant Group (Native,
Late)\footnote{Similarly, we treat late signers as a single group in our analyses and disregard the differing age of acquisition intervals among the late signers (0-3, 4-7, 8-12, 13-17).}.

@@

\begin{figure}
\centering
\includegraphics{manuscript_v2_files/figure-latex/count-plot-1.pdf}
\caption{Referent counts by Discourse Status (Introduction, Maintanence,
Re-introduction), RE Type (Nominal, Pronominal, Classifier, Null), and
Participant Group (Native, Late)}
\end{figure}

For more inference on the data and having pairwise comparisons, we fit a
regression model to RE Type using discourse status and acquisition group
as predictors. We used the brms package (Bürkner, 2018) in R, with a
categorical distribution on the responses and sum contrasts for the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late). As the overall number of produced
pronouns was very little (40 data points), we excluded pronominal use
from the following analyses. For the current analysis, we did not define
priors ourselves and used the preset uninformed priors.
@ref\{fig:model-gram\}\footnote{We ran another model where we used the
  Nativeness predictor with 3 levels 0-3:Native, 4-7:Late1, and
  7-above:Late2. However, our model did not converge properly and the
  credible intervals were very wide spread, yielding the results
  uninformative. We provide the model results as a plot in
  \ref{section:d}.} shows the posterior probability distributions where
the dot is the median estimate, the thick line is the 50\% credible
intervals, and the thin line is the 95\% credible intervals. There are 3
responses we are considering in this model. They are; Classifier,
Nominative, and Null. Classifier response is the level that other
responses Nominative and Null are compared against.

\begin{verbatim}
## Warning: Ignoring unknown aesthetics: height
\end{verbatim}

\begin{figure}
\centering
\includegraphics{manuscript_v2_files/figure-latex/model-gram-1.pdf}
\caption{Regression model plot for the RE Type (Nominal, Null) with the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{manuscript_v2_files/figure-latex/model-camera-1.pdf}
\caption{Regression model plot for the RE Type (Nominal, Null) with the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late)}
\end{figure}

>>>>

We collected 4142 data points as a result of the experiment. Each data
point is a referent tracked by the participant. Each of the REs is
classified in terms of its Discourse Status (Introduction, Maintenance,
Re-introduction), its Type (Nominal, Pronominal, Classifer,
Null)\footnote{In our statistical analyses, we will not consider the subtypes of REs but rather group them by the four proposed main types (Nominal, Pronominal, Classifer, and Null). However, we allude to the numerical distribution of the subtypes in this and following sections.},
and Participant Group (Native,
Late)\footnote{Similarly, we treat late signers as a single group in our analyses and disregard the differing age of acquisition intervals among the late signers (0-3, 4-7, 8-12, 13-17).}.

@@

\begin{figure}
\centering
\includegraphics{revised_manuscript_files/figure-latex/fig:count-plot-1.pdf}
\caption{Referent counts by Discourse Status (Introduction, Maintanence,
Re-introduction), RE Type (Nominal, Pronominal, Classifier, Null), and
Participant Group (Native, Late)}
\end{figure}

For more inference on the data and having pairwise comparisons, we fit a
regression model to RE Type using discourse status and acquisition group
as predictors. We used the brms package (Bürkner, 2018) in R, with a
categorical distribution on the responses and sum contrasts for the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late). As the overall number of produced
pronouns was very little (40 data points), we excluded pronominal use
from the following analyses. For the current analysis, we did not define
priors ourselves and used the preset uninformed priors. Figure
2\footnote{We ran another model where we used the Nativeness predictor
  with 3 levels 0-3:Native, 4-7:Late1, and 7-above:Late2. However, our
  model did not converge properly and the credible intervals were very
  wide spread, yielding the results uninformative. We provide the model
  results as a plot in \ref{section:d}.} shows the posterior probability
distributions where the dot is the median estimate, the thick line is
the 50\% credible intervals, and the thin line is the 95\% credible
intervals. There are 3 responses we are considering in this model. They
are; Classifier, Nominative, and Null. Classifier response is the level
that other responses Nominative and Null are compared against.

\begin{figure}
\centering
\includegraphics{revised_manuscript_files/figure-latex/model-gram-1.pdf}
\caption{Regression model plot for the RE Type (Nominal, Null) with the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late)}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{revised_manuscript_files/figure-latex/model-camera-1.pdf}
\caption{Regression model plot for the RE Type (Nominal, Null) with the
predictors Discourse Status (Introduction, Maintenance, Re-introduction)
and Participant Group (Native, Late)}
\end{figure}
